Maximum Allowable Current Determination of RBS By Using a Directed Graph Model and Greedy Algorithm

### 2023-09-13 paper/SST/SST_main.tex
用于学术润色的版本：删除了中文注释
修改到内容低于6k单词，交付润色机构

% 【version: SST-1.4】

% 【done】 
% =====0909
% 按 Q 修改意见修改 0901 【优先】
% =====0910
% 1. 摘要修改，量化我们的成果：explain the most important achievements of the proposed method quantitatively
% 2. 介绍修改，相关文献：
%   2.1 RBS 结构分析相关的
%   2.2 网络流（最大流）相关（但因为问题不同，无法使用，提一句穷举）
% 3. 介绍修改，逐点列出我们的贡献：state research contribution and achievements as bullet points at the end of the Introduction section
% 4. 讨论修改，增加算法复杂度，以及和穷举法的比较（该领域尚为空白，没有sota的算法）
% 5. 讨论修改，增加算法的 limitations（根据复杂度，大规模不好用）
% 6. 讨论修改，增加结果的准确性介绍（和穷举结果比较）：explain about the accuracy, sufficiency and reliability of their results? How do they verify and validate the results
% 7. 修改算法的第15步
% 8. 重写总结
% 9. 添加文献
% =====0911
% 1. introduction 整体逻辑不流畅，跳跃过大
% 2. introduction 文献
% 2. conclusion 结尾，可以加上一两句说说这个方法的应用价值之类的，吹一吹
% 3. abstract
%   3.1 删去 75000 倍的效率；
%   3.2 凝练一点，就是说这个方法把遍历法中的枚举开关状态组合，转换为了对最短路径的组合；
%   3.3 算法复杂度、效率提升倍数=2^开关数/2^电池数
%   3.4 调整 discussion 的相关内容
% 4. 删去 最大流
% 5. 按 Q 的意见修改
% =====0913
% 1. 按师兄的修改意见修改（0912晚）
% 2. 调整文献顺序，改用 biber

% 【doing】

% 【todo】
% ==18号润色完再次核对，21或22号提交。

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{setspace}
\usepackage[margin=1.25in]{geometry}
\usepackage{graphicx}
% \graphicspath{ {./figures/} }
\graphicspath{ {../figures/} }
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{lineno}
\linenumbers

@@

% \usepackage[final]{changes}
\usepackage[defaultcolor=red]{changes}
% \added{xxx}
% \deleted{xxxx}
% \replaced{a}{b} 原文的b替换成a
% \usepackage{easyReview} % texstudio 部分

@@

%%%%%% Authors %%%%%%
% Authors should be listed in order of contribution to the paper, by first name, then middle initial (if any), followed by last name.
% Authors should be listed in the order in which they will appear in the published version if the manuscript is accepted. 
% Use an asterisk (*) to identify the corresponding author, and be sure to include that person’s e-mail address. Use symbols (in this order: †, ‡, §, ||, ¶, #, ††, ‡‡, etc.) for author notes, such as present addresses, “These authors contributed equally to this work” notations, and similar information.
% You can include group authors, but please include a list of the actual authors (the group members) in the Supplementary Materials.
\author[1$\dag$]{Binghui Xu}
\author[1$\dag$]{Guangbin Hua}
\author[1*]{Cheng Qian}
\author[1,2]{Quan Xia}
\author[1]{Bo Sun}
\author[1]{Yi Ren}
\author[1]{Zili Wang}

%%%%%% Affiliations %%%%%%
\affil[1]{School of Reliability and Systems Engineering, Beihang University, Beijing, 100191, China}
\affil[2]{School of Aeronautic Science and Engineering at Beihang University, Beijing, China}
\affil[*]{Address correspondence to: cqian@buaa.edu.cn}
\affil[$\dag$]{These authors contributed equally to this work.}

@@

The algorithm, as illustrated in Figure \ref{fig:flowchart}, can be summarized as follows, with the corresponding pseudo-code presented in Algorithm \ref{alg:greedy}.
First, the shortest paths ($SP$s) are obtained using Equations \ref{eq:weight} and \ref{eq:def_sp} in conjunction with Dijkstra Search. 
Next, the matrix $\bm{A}$ is calculated using Equation \ref{eq:A}, and the initial $N_{set}$ is set to $N_b$. 
The algorithm iteratively checks different combinations of $c_b$ batteries from $N_b$ and updates $N_{set}$ using a dichotomy method until convergence is reached. 
For each combination, the algorithm constructs an effective solution if possible, and calculates the currents $I_o$ and $\bm{I}_b$ using Equations \ref{eq:I_o} and \ref{eq:I_b}. 
If the maximum current $\bm{I}_b$ is less than or equal to $I_m$, the $\eta$ is calculated using Equation \ref{eq:eta}, and the maximum $\eta$ is updated accordingly. 
Finally, the algorithm outputs the maximum $\eta$ once $N_{set}$ converges.

\tikzset{
  meta box/.style={draw, black, very thick, text centered, },
  punkt/.style={meta box, rectangle, rounded corners, inner sep=.25em, minimum height=2em, minimum width=4em, align=center, text width=10em },
  round/.style={meta box, circle, minimum size=0, inner sep=0pt, outer sep=0pt },
  every fit/.style={draw, thick, dashed, gray, inner xsep=.5em, inner ysep=.75em }
}
\begin{figure}
\begin{tikzpicture}[font=\small, node font=\small, node distance=1.5em]
    \node[punkt]     (input) {Input: RBS structure};
    \node[punkt, below=0.3of input] (get_SP) {get $SP$s by Equations \ref{eq:weight} and \ref{eq:def_sp} and Dijkstra Search};
    \node[punkt, below=0.3of get_SP] (get_A) {get $\bm{A}$ from Equation \ref{eq:A}};
    \node[punkt, below=0.3of get_A] (get_Nset) {init $N_{set}=N_b$ };
    \node[punkt, below=0.3of get_Nset] (get_cb) {get $c_b$s by combinating $N_{set}$ batteries from $N_b$};
    \node[draw, diamond, aspect=2, below=0.3of get_cb] (is_check_all_cb) {are all $c_b$s checked?};
    \node[draw, diamond, aspect=2, right=1of is_check_all_cb] (is_Nset_converged) {is $N_{set}$ converged?};
    \node[punkt, above=of is_Nset_converged] (reset_Nset) {reset $N_{set}$ by dichotomy};
    \node[punkt, text width=15em, below=0.3of is_check_all_cb] (get_Xs) {
        select an unchecked $c_b$, and get its $\bm{X}_m$ by \\ 
        if switch $j$ $\in \bigcup_{i\in c_b}SP_i$:\\
        $\bm{X}[j]=1$ else $0$};
    \node[punkt, below=0.3of get_Xs] (get_Yn) {get $\bm{Y}_n$ by Equation \ref{eq:Yn}};
    \node[draw, diamond, aspect=2, below=0.3of get_Yn] (is_Yn_invertible) {is $\bm{Y}_n$ invertible?};
    \node[punkt, right=1.3of is_Yn_invertible] (construct) {construct an effective solution};
    \node[punkt, below=0.3of is_Yn_invertible] (get_I) {get $I_o$ and $\bm{I}_b$ by Equations \ref{eq:I_o} and \ref{eq:I_b}};
    \node[draw, diamond, aspect=2, below=0.3of get_I] (is_leq_Im) {is $\max \bm{I}_b \leq I_m$?};
    \node[punkt, right=1.3of is_leq_Im] (drop_eta) {drop this $\eta$};
    \node[punkt, below=0.3of is_leq_Im] (get_eta) {get $\eta$ by Equation \ref{eq:eta}};
    \node[punkt, below=0.3of get_eta] (update_max_eta) {update $\max \eta$};
    \node[punkt, right=1of is_Nset_converged] (output) {Output: $\max \eta$};
    \node[round,left=1.5of update_max_eta](point1){};

    \graph{
      (input) -> (get_SP) -> (get_A) -> (get_Nset) -> (get_cb) -> (is_check_all_cb) ->["No"] (get_Xs) -> (get_Yn) -> (is_Yn_invertible) ->["Yes"] (get_I) -> (is_leq_Im) ->["Yes"] (get_eta) -> (update_max_eta);
      (is_check_all_cb) ->["Yes"] (is_Nset_converged) ->["No"] (reset_Nset) -> (get_cb);
      (is_Yn_invertible) ->["No"] (construct) ->[to path={|- (\tikztotarget)}] (get_I);
      (is_leq_Im) ->["No"] (drop_eta) ->[to path={|- (\tikztotarget)}] (update_max_eta);
      (is_Nset_converged) ->["Yes"] (output);
      (update_max_eta) -- (point1) ->[to path={|- (\tikztotarget)}] (is_check_all_cb);
    };
\end{tikzpicture}
\caption{The computational flowchart of the MAC for a given RBS.}\label{fig:flowchart}
\end{figure}

@@

As shown in Figure \ref{fig:study-stru-my}, the new RBS structure consists of 4 batteries and 19 switches. 
The corresponding directed graph is depicted in Figure \ref{fig:study-dirgraph-my}, which is composed of a total of 18 nodes and 43 edges. 
Batteries $B_1$, $B_2$, $B_3$, and $B_4$ are denoted by green directed edges in the graph, while the 19 switches are represented by gray directed edges with bi-directional arrows. 
The external electrical load is treated as a directed edge from the cathode of the RBS (i.e., node 18) to the anode (i.e., node 1), as indicated by the blue directed edge in the graph.
Utilizing Equation \ref{eq:weight} and the Dijkstra algorithm, the $SP$s of the four batteries in the RBS structure of Figure \ref{fig:study-stru-my} are highlighted by red in Figures \ref{fig:sp1}-\ref{fig:sp4}.
Finally, the MAC calculation results of the structure in Figure \ref{fig:study-stru-my} are shown as Table \ref{tab:study-results-my} and Figure \ref{fig:study-results-my}, obtained by the greedy algorithm \ref{alg:greedy}.
Table \ref{tab:study-results-my} contains the switches states, the output current $I_o$, battery current $\bm{I}_b$ and ratio $\eta$ of the RBS structure with all batteries in good health when the RBS output reaches the MAC.
Figure \ref{fig:study-results-my} presents the corresponding circuit, with the red highlight indicating that current is flowing through the respective branches.

@@

\added{
From the literature research we have conducted, no formal report on the algorithm for MAC in RBS has been found yet.
The brute force algorithm, which goes through all possible switch states, is the most straightforward way to solve the MAC problem and is used as a benchmark for the proposed greedy algorithm.
Assuming that a RBS has $N_b$ batteries and $N_s$ switches, and the corresponding directed graph has $N$ nodes, it requires $2^{N_s}$ iterations to traverse all reconfigured structures.
The calculation for each reconfigured structure by Equations \ref{eq:I_o}-\ref{eq:eta} requires matrix inversion and matrix multiplication, with a time complexity of $O(N^3+2N^2N_b+N^2N_s+NN^2_b)$.
Therefore, the time complexity of the brute force algorithm is $O(2^{N_s}(N^3+2N^2N_b+N^2N_s+NN^2_b))$.
The greedy algorithm proposed in this paper requires find the $SP$ for each battery, which requires $N_b$ iterations.
Each $SP$ can be obtained by couple Dijkstra algorithms.
Therefore, the total time complexity of calculating all $SP$s is $O(2N_b(N_b+2N_s)\log N)$.
According to the Appendix \ref{alg:greedy}, the RBS can reconfigure $C^{N_{set}}_{N_b}$ structures by selecting $N_{set}$ batteries from $N_b$ batteries, which is $\sum^{N_b}_{N_{set}=1}C^{N_{set}}_{N_b}/N_b \approx 2^{N_b}/N_b$ on average.
Hence, with bisection method, the time complexity of the greedy algorithm is $O(2^{N_b}/N_b(N^3+2N^2N_b+N^2N_s+NN^2_b)\log N_b+2N_b(N_b+2N_s)\log N)$, i.e., $O(2^{N_b}/N_b(N^3+2N^2N_b+N^2N_s+NN^2_b)\log N_b)$.
Based on currently proposed RBS structures\cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711}, the number of batteries $N_b$, switches $N_s$, and nodes $N$ have the following quantitative relationships: $N_s \approx (3\sim 5)N_b$, $N \approx N_s$. 
After simplifying, the time complexity of the greedy algorithm is $O(2^{N_b}N_s^2\log N_b)$, while it is $O(2^{N_s}N_s^3)$ for brute force algorithm.
Therefore, it is reasonable to believe that as the size of the RBS increases, especially the number of the switches, the greedy algorithm will have an advantage over the algorithm that goes through all reconfigured structures.
This can be confirmed from the number of structures required for MAC determination in the previous subsection. 
Compared to the brute force algorithm, the efficiency of the method based on the greedy algorithm has been improved by 3000 to 75000 times, which is theoretically $N_s 2^{N_s - N_b} \log N_b$ times according to the above time complexity analysis.
Among the three RBS structures, the highest is the RBS structure with 19 switches (Figure \ref{fig:study-stru-my}).
This benefit from two key points:
(1) The $SP$s guide the RBS to reconfigure reasonable structures, rather than blindly going through all possible structures. This reduces the factor in complexity from $2^{N_s}$ to $2^{N_b}$, which is the main reason for the improvement in efficiency;
(2) The bisection method further accelerates this process.
However, the greedy algorithm proposed in this paper still contains exponential terms in the time complexity, which means it may not be able to handle extremely large-scale RBS structures.
}

@@

\begin{algorithm}
    \caption{Get the max available currents of a certain RBS}\label{alg:greedy}
    \KwData{Directed graph model $G(V,E)$ of the RBS}
    \KwResult{$\max \eta$}
    \For{$i \in E_b$}{
        $P_i \leftarrow \{path| \text{starts at $v_1$ and ends at $v_n$} \}$\;
        $SP_i \leftarrow p_i \text{ which has the minimum}~\omega(p_i)~\text{among all}~p_i \in P_i. $
    }
    get $\bm{A}$ by Equation \ref{eq:A}\;
    \While{not yet determine $\max \eta$ }
    {
        $N_{set} \leftarrow \text{number of setected $SP$s calculated by dichotomy}$\;
        $C_b    \leftarrow \text{set of all combinations of $N_{set} $~batteries from $N_b$}$\;
        \For{$c_b \in C_b$}{
            $\bm{x}_s \leftarrow \text{list of all switches' state: $x_s[j]=1$ if $ j \in \bigcup_{i\in c_b}SP_i $ else 0}$\;
            $\bm{X} \leftarrow diag[1,1,\cdots,1,\bm{x}_s] $\;
            get $\bm{Y}_n$ by Equation \ref{eq:Yn}\;
            \eIf{$\bm{Y}_n$ is invertible}{
              \added{pass}
            }{construct an effective solution}
            get $I_o$ by Equation \ref{eq:I_o}\;
            get $\bm{I}_b$ by Equation \ref{eq:I_b}\;
            \eIf{$\max(\bm{I}_b)\leq I_m$}{
                $\eta \leftarrow I_o/\max(\bm{I}_b)$\;
            }{break}
        }
    }
\end{algorithm}

\section*{Acknowledgments}

\subsection*{Author Contributions}

B. Xu conceived the main idea, formulated the overarching research goals and aims, designed the algorithm, and reviewed and revised the manuscript.
G. Hua developed and analyzed the model, implemented the code and supporting algorithms, and wrote the initial draft.
C. Qian provided critical review, commentary, and revisions.
Q. Xia contributed to shaping the research, analysis, and manuscript.
B. Sun conducted the research and investigation process.
Y. Ren secured the funding and supervised the project.
Z. Wang verified the results and provided necessary resources.

\subsection*{Funding}

This work was supported by the National Natural Science Foundation of China (NSFC, No.52075028).

\subsection*{Conflicts of Interest}

The authors declare that there is no conflict of interest regarding the publication of this article.

\subsection*{Data Availability}

This work does not require any data to be declared or publicly disclosed.

@@

\printbibliography

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{setspace}
\usepackage[margin=1.25in]{geometry}
\usepackage{graphicx}
% \graphicspath{ {./figures/} }
\graphicspath{ {../figures/} }
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{lineno}
% \linenumbers

@@

\usepackage[final]{changes}
% \usepackage[defaultcolor=red]{changes}
% \added{xxx}
% \deleted{xxxx}
% \replaced{a}{b}

@@

%%%%%% Authors %%%%%%
% Authors should be listed in order of contribution to the paper, by first name, then middle initial (if any), followed by last name.
% Authors should be listed in the order in which they will appear in the published version if the manuscript is accepted. 
% Use an asterisk (*) to identify the corresponding author, and be sure to include that person’s e-mail address. Use symbols (in this order: †, ‡, §, ||, ¶, #, ††, ‡‡, etc.) for author notes, such as present addresses, “These authors contributed equally to this work” notations, and similar information.
% You can include group authors, but please include a list of the actual authors (the group members) in the Supplementary Materials.
\author[1]{30577}
% \author[1$\dag$]{Binghui Xu}
% \author[1$\dag$]{Guangbin Hua}
% \author[1*]{Cheng Qian}
% \author[1,2]{Quan Xia}
% \author[1]{Bo Sun}
% \author[1]{Yi Ren}
% \author[1]{Zili Wang}

%%%%%% Affiliations %%%%%%
% \affil[1]{School of Reliability and Systems Engineering, Beihang University, Beijing, 100191, China}
% \affil[2]{School of Aeronautic Science and Engineering at Beihang University, Beijing, China}
% \affil[*]{Address correspondence to: cqian@buaa.edu.cn}
% \affil[$\dag$]{These authors contributed equally to this work.}

@@

The algorithm, as illustrated in Figure \ref{fig:flowchart}, can be summarized as follows, with the corresponding pseudo-code presented in Algorithm 1. % \ref{alg:greedy}.
First, the shortest paths ($SP$s) are obtained using Equations \ref{eq:weight} and \ref{eq:def_sp} in conjunction with Dijkstra Search. 
Next, the matrix $\bm{A}$ is calculated using Equation \ref{eq:A}, and the initial $N_{set}$ is set to $N_b$. 
The algorithm iteratively checks different combinations of $c_b$ batteries from $N_b$ and updates $N_{set}$ using a dichotomy method until convergence is reached. 
For each combination, the algorithm constructs an effective solution if possible, and calculates the currents $I_o$ and $\bm{I}_b$ using Equations \ref{eq:I_o} and \ref{eq:I_b}. 
If the maximum current $\bm{I}_b$ is less than or equal to $I_m$, the $\eta$ is calculated using Equation \ref{eq:eta}, and the maximum $\eta$ is updated accordingly. 
Finally, the algorithm outputs the maximum $\eta$ once $N_{set}$ converges.

% \tikzset{
%   meta box/.style={draw, black, very thick, text centered, },
%   punkt/.style={meta box, rectangle, rounded corners, inner sep=.25em, minimum height=2em, minimum width=4em, align=center, text width=10em },
%   round/.style={meta box, circle, minimum size=0, inner sep=0pt, outer sep=0pt },
%   every fit/.style={draw, thick, dashed, gray, inner xsep=.5em, inner ysep=.75em }
% }
% \begin{figure}
% \begin{tikzpicture}[font=\small, node font=\small, node distance=1.5em]
%     \node[punkt]     (input) {Input: RBS structure};
%     \node[punkt, below=0.3of input] (get_SP) {get $SP$s by Equations \ref{eq:weight} and \ref{eq:def_sp} and Dijkstra Search};
%     \node[punkt, below=0.3of get_SP] (get_A) {get $\bm{A}$ from Equation \ref{eq:A}};
%     \node[punkt, below=0.3of get_A] (get_Nset) {init $N_{set}=N_b$ };
%     \node[punkt, below=0.3of get_Nset] (get_cb) {get $c_b$s by combinating $N_{set}$ batteries from $N_b$};
%     \node[draw, diamond, aspect=2, below=0.3of get_cb] (is_check_all_cb) {are all $c_b$s checked?};
%     \node[draw, diamond, aspect=2, right=1of is_check_all_cb] (is_Nset_converged) {is $N_{set}$ converged?};
%     \node[punkt, above=of is_Nset_converged] (reset_Nset) {reset $N_{set}$ by dichotomy};
%     \node[punkt, text width=15em, below=0.3of is_check_all_cb] (get_Xs) {
%         select an unchecked $c_b$, and get its $\bm{X}_m$ by \\ 
%         if switch $j$ $\in \bigcup_{i\in c_b}SP_i$:\\
%         $\bm{X}[j]=1$ else $0$};
%     \node[punkt, below=0.3of get_Xs] (get_Yn) {get $\bm{Y}_n$ by Equation \ref{eq:Yn}};
%     \node[draw, diamond, aspect=2, below=0.3of get_Yn] (is_Yn_invertible) {is $\bm{Y}_n$ invertible?};
%     \node[punkt, right=1.3of is_Yn_invertible] (construct) {construct an effective solution};
%     \node[punkt, below=0.3of is_Yn_invertible] (get_I) {get $I_o$ and $\bm{I}_b$ by Equations \ref{eq:I_o} and \ref{eq:I_b}};
%     \node[draw, diamond, aspect=2, below=0.3of get_I] (is_leq_Im) {is $\max \bm{I}_b \leq I_m$?};
%     \node[punkt, right=1.3of is_leq_Im] (drop_eta) {drop this $\eta$};
%     \node[punkt, below=0.3of is_leq_Im] (get_eta) {get $\eta$ by Equation \ref{eq:eta}};
%     \node[punkt, below=0.3of get_eta] (update_max_eta) {update $\max \eta$};
%     \node[punkt, right=1of is_Nset_converged] (output) {Output: $\max \eta$};
%     \node[round,left=1.5of update_max_eta](point1){};
% 
%     \graph{
%       (input) -> (get_SP) -> (get_A) -> (get_Nset) -> (get_cb) -> (is_check_all_cb) ->["No"] (get_Xs) -> (get_Yn) -> (is_Yn_invertible) ->["Yes"] (get_I) -> (is_leq_Im) ->["Yes"] (get_eta) -> (update_max_eta);
%       (is_check_all_cb) ->["Yes"] (is_Nset_converged) ->["No"] (reset_Nset) -> (get_cb);
%       (is_Yn_invertible) ->["No"] (construct) ->[to path={|- (\tikztotarget)}] (get_I);
%       (is_leq_Im) ->["No"] (drop_eta) ->[to path={|- (\tikztotarget)}] (update_max_eta);
%       (is_Nset_converged) ->["Yes"] (output);
%       (update_max_eta) -- (point1) ->[to path={|- (\tikztotarget)}] (is_check_all_cb);
%     };
% \end{tikzpicture}
% \caption{The computational flowchart of the MAC for a given RBS.}\label{fig:flowchart}
% \end{figure}

\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{flowchart.jpg}
    \caption{The computational flowchart of the MAC for a given RBS.}\label{fig:flowchart}
\end{figure}

@@

As shown in Figure \ref{fig:study-stru-my}, the new RBS structure consists of 4 batteries and 19 switches. 
The corresponding directed graph is depicted in Figure \ref{fig:study-dirgraph-my}, which is composed of a total of 18 nodes and 43 edges. 
Batteries $B_1$, $B_2$, $B_3$, and $B_4$ are denoted by green directed edges in the graph, while the 19 switches are represented by gray directed edges with bi-directional arrows. 
The external electrical load is treated as a directed edge from the cathode of the RBS (i.e., node 18) to the anode (i.e., node 1), as indicated by the blue directed edge in the graph.
Utilizing Equation \ref{eq:weight} and the Dijkstra algorithm, the $SP$s of the four batteries in the RBS structure of Figure \ref{fig:study-stru-my} are highlighted by red in Figures \ref{fig:sp1}-\ref{fig:sp4}.
Finally, the MAC calculation results of the structure in Figure \ref{fig:study-stru-my} are shown as Table \ref{tab:study-results-my} and Figure \ref{fig:study-results-my}, obtained by the greedy algorithm 1. % \ref{alg:greedy}.
Table \ref{tab:study-results-my} contains the switches states, the output current $I_o$, battery current $\bm{I}_b$ and ratio $\eta$ of the RBS structure with all batteries in good health when the RBS output reaches the MAC.
Figure \ref{fig:study-results-my} presents the corresponding circuit, with the red highlight indicating that current is flowing through the respective branches.

@@

\added{
From the literature research we have conducted, no formal report on the algorithm for MAC in RBS has been found yet.
The brute force algorithm, which goes through all possible switch states, is the most straightforward way to solve the MAC problem and is used as a benchmark for the proposed greedy algorithm.
Assuming that a RBS has $N_b$ batteries and $N_s$ switches, and the corresponding directed graph has $N$ nodes, it requires $2^{N_s}$ iterations to traverse all reconfigured structures.
The calculation for each reconfigured structure by Equations \ref{eq:I_o}-\ref{eq:eta} requires matrix inversion and matrix multiplication, with a time complexity of $O(N^3+2N^2N_b+N^2N_s+NN^2_b)$.
Therefore, the time complexity of the brute force algorithm is $O(2^{N_s}(N^3+2N^2N_b+N^2N_s+NN^2_b))$.
The greedy algorithm proposed in this paper requires find the $SP$ for each battery, which requires $N_b$ iterations.
Each $SP$ can be obtained by couple Dijkstra algorithms.
Therefore, the total time complexity of calculating all $SP$s is $O(2N_b(N_b+2N_s)\log N)$.
According to the Appendix 1, % \ref{alg:greedy},
the RBS can reconfigure $C^{N_{set}}_{N_b}$ structures by selecting $N_{set}$ batteries from $N_b$ batteries, which is $\sum^{N_b}_{N_{set}=1}C^{N_{set}}_{N_b}/N_b \approx 2^{N_b}/N_b$ on average.
Hence, with bisection method, the time complexity of the greedy algorithm is $O(2^{N_b}/N_b(N^3+2N^2N_b+N^2N_s+NN^2_b)\log N_b+2N_b(N_b+2N_s)\log N)$, i.e., $O(2^{N_b}/N_b(N^3+2N^2N_b+N^2N_s+NN^2_b)\log N_b)$.
Based on currently proposed RBS structures\cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711}, the number of batteries $N_b$, switches $N_s$, and nodes $N$ have the following quantitative relationships: $N_s \approx (3\sim 5)N_b$, $N \approx N_s$. 
After simplifying, the time complexity of the greedy algorithm is $O(2^{N_b}N_s^2\log N_b)$, while it is $O(2^{N_s}N_s^3)$ for brute force algorithm.
Therefore, it is reasonable to believe that as the size of the RBS increases, especially the number of the switches, the greedy algorithm will have an advantage over the algorithm that goes through all reconfigured structures.
This can be confirmed from the number of structures required for MAC determination in the previous subsection. 
Compared to the brute force algorithm, the efficiency of the method based on the greedy algorithm has been improved by 3000 to 75000 times, which is theoretically $N_s 2^{N_s - N_b} \log N_b$ times according to the above time complexity analysis.
Among the three RBS structures, the highest is the RBS structure with 19 switches (Figure \ref{fig:study-stru-my}).
This benefit from two key points:
(1) The $SP$s guide the RBS to reconfigure reasonable structures, rather than blindly going through all possible structures. This reduces the factor in complexity from $2^{N_s}$ to $2^{N_b}$, which is the main reason for the improvement in efficiency;
(2) The bisection method further accelerates this process.
However, the greedy algorithm proposed in this paper still contains exponential terms in the time complexity, which means it may not be able to handle extremely large-scale RBS structures.
}

@@

% \begin{algorithm}
%     \caption{Get the max available currents of a certain RBS}\label{alg:greedy}
%     \KwData{Directed graph model $G(V,E)$ of the RBS}
%     \KwResult{$\max \eta$}
%     \For{$i \in E_b$}{
%         $P_i \leftarrow \{path| \text{starts at $v_1$ and ends at $v_n$} \}$\;
%         $SP_i \leftarrow p_i \text{ which has the minimum}~\omega(p_i)~\text{among all}~p_i \in P_i. $
%     }
%     get $\bm{A}$ by Equation \ref{eq:A}\;
%     \While{not yet determine $\max \eta$ }
%     {
%         $N_{set} \leftarrow \text{number of setected $SP$s calculated by dichotomy}$\;
%         $C_b    \leftarrow \text{set of all combinations of $N_{set} $~batteries from $N_b$}$\;
%         \For{$c_b \in C_b$}{
%             $\bm{x}_s \leftarrow \text{list of all switches' state: $x_s[j]=1$ if $ j \in \bigcup_{i\in c_b}SP_i $ else 0}$\;
%             $\bm{X} \leftarrow diag[1,1,\cdots,1,\bm{x}_s] $\;
%             get $\bm{Y}_n$ by Equation \ref{eq:Yn}\;
%             \eIf{$\bm{Y}_n$ is invertible}{
%               \added{pass}
%             }{construct an effective solution}
%             get $I_o$ by Equation \ref{eq:I_o}\;
%             get $\bm{I}_b$ by Equation \ref{eq:I_b}\;
%             \eIf{$\max(\bm{I}_b)\leq I_m$}{
%                 $\eta \leftarrow I_o/\max(\bm{I}_b)$\;
%             }{break}
%         }
%     }
% \end{algorithm}
\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{algorithm.jpg}
\end{figure}

% 
% \section*{Acknowledgments}
% 
% \subsection*{Author Contributions} 
% 
% B. Xu conceived the main idea, formulated the overarching research goals and aims, designed the algorithm, and reviewed and revised the manuscript.
% G. Hua developed and analyzed the model, implemented the code and supporting algorithms, and wrote the initial draft.
% C. Qian provided critical review, commentary, and revisions.
% Q. Xia contributed to shaping the research, analysis, and manuscript.
% B. Sun conducted the research and investigation process.
% Y. Ren secured the funding and supervised the project.
% Z. Wang verified the results and provided necessary resources.
% 
% \subsection*{Funding}
% 
% This work was supported by the National Natural Science Foundation of China (NSFC, No.52075028).
% 
% \subsection*{Conflicts of Interest}
% 
% The authors declare that there is no conflict of interest regarding the publication of this article.
% 
% \subsection*{Data Availability}
% 
% This work does not require any data to be declared or publicly disclosed.

@@

% \printbibliography
